%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Rex Posadas} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> 1724 Lady Grey Avenue,\\ % Address line 1
\> Pflugerville, TX  78660 \\ % Address line 2
% {\bf Date of Birth} \> 7$^{th}$ September 1979 \\ % Date of birth 
% {\bf Nationality} \> British % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
% {\bf Home Phone} \> +0 (000) 111 1111 \\ % Home phone
{\bf Mobile Phone} \> 737 228 3482 \\ % Mobile phone
{\bf Email} \> \href{mailto:rexposadas@gmail.com}{rexposadas@gmail.com} \\ % Email address
\end{tabbing}}



%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{Jan 2019 -}{Present}
{Contractor, Austin, TX}
{}
{Engineering Manager/Technical Team Lead}
{\\

\begin{itemize-noindent}
\item{Key personnel in client's product execution: From concept, to managing a distributed team and software around it and then delivering the product to the market.}
\item{Led distributed team using Agile. Managed Scrum meetings and sprint goals.}
\item{Technologies used included AWS, Google Cloud Platform, Makefiles, Kubernetes, Docker, Golang and Postgres.}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Sep 2014 -}{Dec 2018}
{Agrarian Labs, Austin, TX}
{}
{Co-founder and Head of Engineering}
{

\begin{itemize-noindent}
\item{Architected a high-volume IoT application.  The application receives over 10Gigs of data per day from IoT devices distributed across the United States.}
\item{Executive team member responsible for technical recruiting. Recruiting strategies included organizing a technical Meetup and participating in South by Southwest (SXSW is an Austin conference and festival).}
\item{We were finalists in SXSW in the Enterprise and Smart Data category.}
\item{Technology used included AWS, Kubernetes, Docker, Makefiles, Golang, DynamoDB and Postgres, Redis, and Swift (mobile on iOS).}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Apr 2014 -}{Dec 2014}
{MomentumSI (acquired by VMWare), Austin, TX}
{}
{Senior Engineer}
{
\begin{itemize-noindent}
\item{Built a Linux container management system using Go, NSQ, Docker and the ELK stack.}
\item{Contributed documentation and Docker images to the NSQ open-source project.}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Oct 2013 -}{Dec 2014}
{Vubeology, Austin, TX}
{}
{Senior Engineer}
{
\begin{itemize-noindent}
\item{Built a mission critical advertising module for a video streaming platform. Response times for serving advertisements are in the 10-millisecond range.} 
\item{Established a baseline product quality by creating a simulation engine.} 
\item{Created a Map-Reduce module for aggregating metrics data.}
\end{itemize-noindent}
}


%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Programming Languages}
{
\textit{Ruby} - MRI 1.8.7, 1.9.2\\
\textit{ASP.NET, C\#, VB.NET}\\
\textit{PHP}\\
\textit{Java/Scala}
}

%------------------------------------------------

\skillgroup{Web Development}
{
\textit{HTML5, CSS3/SASS, JavaScript/CoffeeScript/jQuery}\\
\textit{Ruby on Rails v3.1}\\
\textit{Test:Unit, RSpec, Cucumber, Selenium} - automated testing frameworks\\
\textit{Apache/Nginx Web Servers}\\
}

%------------------------------------------------

\skillgroup{Miscellaneous}
{
\textit{Microsoft SQL Server 2000/2005} - database architecture and administration\\
\textit{Transact-SQL} - data definition and manipulation\\
\textit{SQL Profiler} - performance tuning and debugging\\
\textit{MySQL Server}\\
\textit{CVS, DARCS, git} - source version control
}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\interestsgroup{
\interest{Badminton, Tennis, Running, Cycling, Sailing}
\interest{Travelling}
\interest{Creative Writing}
\interest{Photography}
\interest{Car Mechanics}
}

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Bill Lumbergh \\ % Referee name
{\bf Company} \> Initech Inc. \\ % Referee company
{\bf Position} \> Vice President \\ % Referee job title 
{\bf Contact} \> \href{mailto:bill@initech.com}{bill@initech.com} % Referee contact information
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Michael "Big Mike" Tucker\\ % Referee name
{\bf Company} \> Burbank Buy More \\ % Referee company
{\bf Position} \> Store Manager \\ % Referee job title 
{\bf Contact} \> \href{mailto:mike@buymore.com}{mike@buymore.com} % Referee contact information
\end{tabbing}}

%----------------------------------------------------------------------------------------

\end{document}